---
title: 'Peer-graded Assignment: R Markdown Presentation & Plotly'
author: "Mochamad Gilang Saputra"
date: "January 3, 2020"
output:
  beamer_presentation: default
  ioslides_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


Peer-graded Assignment: R Markdown Presentation & Plotly

Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity!

Developing Data Products
R Markdown Presentation & Plotly
Peer-graded Assignment.



```{r library, echo = TRUE}
library(plotly)
```

## Slide with Plot
```{r plot}
data(iris)

plot_ly(x= iris$Sepal.Width, y= iris$Sepal.Length, z = iris$Species, 
type = "scatter3d", mode = "markers", color = iris$Species)
```

